\addcontentsline{toc}{chapter}{Литература}
\begin{thebibliography}{99}

    \bibitem{erosion}
    \emph{Xing M., Decaudin P., Baogang H.} Fast Hydraulic Erosion Simulation and Visualization on GPU
    Pacific Graphics, 2007.

    \bibitem{surgery}
    \emph{Gregory J., Kerwin T., Hittle B., Stredney D., Welling B.} Improvement in Realism of a Temporal Bone Dissection Simulator.
    IEEE Transactions on Visualization and Computer Graphics, pp. 747-758, September/October, 2009

    \bibitem{sculpt}
    \emph{Müller J.} Volume Modelling And Rendering Based On 3D Voxel Grids.
    Institut für Computervisualistik Universität Koblenz-Landau, 2005.

    \bibitem{graphics_gems}
    \emph{Glassner A.} Graphics gems. Volume 1 of The graphics gems series.
    Morgan Kaufmann, 1993.

    \bibitem{halfedge}
    \emph{Weiler K.} Edge-based data structures for solid modeling in a curved surface environment. 
    IEEE Comput. Graph. Appl., 5(1):21-40, 1985.

    \bibitem{point_cloud}
    \emph{Rusinkiewicz S., Levoy M.} QSplat: a multiresolution point rendering system for large meshes.
    Proceedings of the 27th annual conference on Computer graphics and interactive techniques, 2000.
   
    \bibitem{mandel}
    \emph{Бенуа Б.} Мандельброт Фрактальная геометрия природы
    М.: Институт компьютерных исследований, 2002.

    \bibitem{gpu_octree}
    \emph{Lefebvre S., Hornus S.} Octree Textures on the GPU structure
    NVIDIA Corporation, GPU Gems 2, 2005.

    \bibitem{gpu_hash}
    \emph{Lefebvre S., Hoppe H.} Perfect spatial hashing.
    ACM Transactions on Graphics (Proc. SIGGRAPH 2006), 25(3), 579-588.

    \bibitem{voxel_rle}
    \emph{Forstmann S., Moll S., Ohya J.} Visualization of large RLE-encoded voxel volumes.
    FIT 2007 ( Technical Report ), Nagoya, Japan, 2007.

    \bibitem{svo_olick}
    \emph{Olick J.} Next Generation Parallelism in Games 
    ACM SIGGRAPH, 2008.

    \bibitem{merks_coral}
    Merks R., Hoekstra A., Kaandorp J. and Sloot P. Spontaneous Branching in a Polyp Oriented Model of Coral Growth.
    ICCS 2002. LCNS 2329, 88–96

    \bibitem{cg:2005}
    Cg Toolkit User's Manual.
    NVIDIA Corporation, 2005.

    \bibitem{cuda_guide}
    NVIDIA CUDA Programming Guide.
    NVIDIA Corporation, 2007.

    \bibitem{cuda_struct_alg}
    \emph{Owens J.}  Data-parallel Algorithms and Data Structures.
    http://www.gpgpu.org/sc2007/

    \bibitem{cuda_optim}
    \emph{Harris M.}  Optimizing CUDA.
    http://www.gpgpu.org/sc2007/

    \bibitem{quant_normals}
    \emph{Baptista R.}  Higher Accuracy Quantized Normals.
    http://www.gamedev.net/reference/articles/article1252.asp

\end{thebibliography}